---
title:  | 
  | Stroop Color-Word Test
  | Scoring Report
date: '`r paste("Report Date: ", Sys.Date())`'
always_allow_html: yes
pagetitle: "Stroop Color-Word Test Scoring Report"
output: 
    word_document:
      df_print: default
      toc: yes
      toc_depth: '4'
    html_document:
      toc: true
      toc_depth: 3
      toc_float: true
      self_contained: yes
      mode: selfcontained
      theme: journal
    pdf_document:
      df_print: default
      toc: yes
header-includes:
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \fancyhead[C]{Sattler-Stoelting Developmental Checklist}
  - \fancyfoot[C]{CONFIDENTIAL REPORT}
  - \fancyfoot[L]{\thepage}
  - \usepackage{comment}
  - \usepackage{float}
  - \usepackage{booktabs}
  - \usepackage{makecell}
#runtime: shiny
params:
  report_format: NA
  t_score_df: NA
  demographics_inputs: NA
  scoring_inputs: NA
  t_score_plots: NA
  raw_score_names_interference: NA
  raw_score_names: NA
  interpretation_text: NA
  narrative_text: NA
---
```{r setup, include=F}
# Libraries
library(kableExtra)
library(flextable)

# Global options
knitr::opts_chunk$set(echo = FALSE)
flextable::set_flextable_defaults(fonts_ignore=TRUE) # or get warnings

# Printing options depending on report format
if(params$report_format == 'html'){
  options(knitr.table.format = 'html')
  } else if (params$report_format == 'pdf') {
    options(knitr.table.format = 'latex')
  } else {
    options(knitr.table.format = 'markdown')
  }
```

`r if(params$report_format != "docx") {"\\begin{comment}"}`

# Stroop Color-Word Test Scoring Report

`r if(params$report_format != "docx") {"\\end{comment}"}`

`r colorize("Demonstration App Only! Not accurate scoring! Get full app at stoeltingco.com", "red")`

## Background Information

```{r background_table, results = 'asis'}
params$demographics_inputs %>%
  cbind.data.frame(., params$scoring_inputs %>% select(-params$raw_score_names)) -> demographic_df
if (params$report_format == "html"){
  demographic_df %>% 
  table_print(colnames = colnames(.), caption = "Demographics", output_format = params$report_format)
} else {
  demographic_df %>% 
  table_print(colnames = colnames(.), caption = "Demographics", output_format = params$report_format, size = 6)
}
```


`r if(params$report_format == "pdf") {"\\begin{comment}"}`

<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 20px;}
</style>
<div class = 'blue'>

`r params$narrative_text`

</div>
`r if(params$report_format == "pdf") {"\\end{comment}"}`

`r if(params$report_format != "pdf") {"\\begin{comment}"}`

`r params$narrative_text`

`r if(params$report_format != "pdf") {"\\end{comment}"}`

## Results

### Overall

``` {r scoring_table}
params$t_score_df %>%
  cbind.data.frame(tibble(scale = "T-score"), .) -> score_df
if(params$report_format == "html"){
  score_df %>% 
    table_print(colnames = c("Scale", gsub(" .*", "", params$raw_score_names_interference)), caption = "T-Scores", output_format = params$report_format)
} else {
  score_df %>% 
    table_print(colnames = c("Scale", gsub(" .*", "", params$raw_score_names_interference)), caption = "T-Scores", output_format = params$report_format, size = 8)
}
```


### Individual Scales
```{r individual_print, results='asis'}
lapply(1:4, function(i) {
  if(params$report_format == "html"){
    cat(paste("<h4>", gsub(" .*", "", rev(params$raw_score_names_interference)[i]), "</h4>"))
    cat("<div class = 'row h-100'>")
      cat("<div class = 'col-md-6'>")
        invisible(print(params$t_score_plots[[i]]))
      cat("</div>")
      cat("<div class = 'col-md-6'>")
        invisible(cat(params$interpretation_text[[i]]))
      cat("</div>")
    cat("</div>")
  } else {
    cat(paste("<h4>", gsub(" .*", "", rev(params$raw_score_names_interference)[i]), "</h4>"))
    invisible(print(params$t_score_plots[[i]]))
    cat("\n")
    invisible(cat(params$interpretation_text[[i]]))
  }
})-> out
```

<!-- insert logo -->
```{r, echo=FALSE, message=F, warning=F, fig.align="center", out.width= '50%', out.height= '50%'}
# Add logo to output
library(jpeg)
library(grid)
library(gridExtra)
url <- "https://stoeltingco.com/Psychological/media/stoelting_logo.jpg"
z <- tempfile()
download.file(url,z,mode="wb")
img <- readJPEG(z)
rimg <- rasterGrob(as.raster(img)) # raster multilayer object
tg <- textGrob("Stoelting Psychology", gp=gpar(fontfamily = "serif", fontsize = 20))
sg1 <- textGrob("www.stoeltingco.com", gp=gpar(fontfamily = "sans", fontsize = 10))
sg2 <- textGrob("620 Wheat Lane", gp=gpar(fontfamily = "sans", fontsize = 10))
sg3 <- textGrob("Wood Dale, IL, USA 60191", gp=gpar(fontfamily = "sans", fontsize = 10))
sg4 <- textGrob("psychtests@stoeltingco.com", gp=gpar(fontfamily = "sans", fontsize = 10))
sg5 <- textGrob("630-860-9700", gp=gpar(fontfamily = "sans", fontsize = 10))
lay <- rbind(c(1,NA),
             c(1,NA),
             c(1,NA),
             c(1,NA),
             c(1,2),
             c(1,3),
             c(1,4),
             c(1,5),
             c(1,6),
             c(1,7),
             c(1,NA),
             c(1,NA),
             c(1,NA),
             c(1,NA))
grid.arrange(rimg, tg, sg1, sg2, sg3, sg4, sg5, layout_matrix = lay)
grid.rect(width = 1.5, height = .5, gp = gpar(lwd = 2, col = "blue", fill = NA))
```
&nbsp;

<!-- html contact links footer -->
```{r contact_info, echo=FALSE, results= 'asis'}
  cat("<p style=\"text-align: 
      center;\">Copyright 2021:<a href=\"https://www.stoeltingco.com\" target = \"_blank\">Stoelting</a></p>")
if (params$report_format == "html"){
  cat("<p style=\"text-align: center;\"><a style=\"color: #0645AD;\" href = \"mailto:psychtests@stoeltingco?subject = Stroop App&body = Message\"><em>Email Stoelting for support</em></a></p>")
}
```



